\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{chngcntr}
\usepackage{float}
\usepackage{tabu}
\usepackage{bm}
\usepackage[lite]{amsrefs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{hyperref}\usepackage{xcolor}
%\graphicspath{ {./img/} }


\counterwithin*{equation}{section}

\newcommand{\R}{\mathbb{R}}

\makeatletter
\newcommand*\bigcdot{\mathpalette\bigcdot@{1}}
\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\makeatother

\usepackage{afterpage}

\newcommand\blankpage{%
    \null
    \thispagestyle{empty}%
    \addtocounter{page}{-1}%
    \newpage}
    
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

%\setlength{\parindent}{0pt}

\DeclareMathOperator*{\argmax}{\arg\!\max}
\DeclareMathOperator*{\argmin}{\arg\!\min}

\newcommand*{\defeq}{\mathrel{\vcenter{\baselineskip0.5ex \lineskiplimit0pt
                     \hbox{\scriptsize.}\hbox{\scriptsize.}}}%
                     =}


\begin{document}
\title{Revised Personal Standpoint}
\author{18-940-270}
\date{}

\maketitle
	Disclaimer: I'm still figuring some stuff out. 
	
	I think it is unethical to perform medical experiments on macaques.
	
	The reasoning is as follows: 
	
	\textbf{1.} As it stands, I think We afford rights to all human beings (ignoring fetuses etc.). Furthermore We afford them to human beings whether they are moral patients or moral agents. The point of this premise is to establish that rights \textit{are} being used to some extent in today's society.
	
	\textbf{2.} I don't think We afford humans rights just because  they are human. We afford humans rights because they are "subjects of a life", i.e. they have a life that matters to them, they have a wellbeing which is to say they have interests which can be satisfied or frustrated etc.
	
	\textbf{3.} By the argument from marginal cases, there are no morally relevant criteria We could use as an excuse not to extend these same rights to most animals, and certainly not an animal as close to us as macaques are. Speciecism certainly does not cut the mustard.
	
	\textbf{4.} Therefore, by not extending rights to macaques We would be ethically inconsistent, and therefore We \textit{should} extend rights to macaques.
	
	\textbf{5.} Medically experimenting upon macaques would infringe on their rights and is therefore ethically wrong.

	
\end{document} 