\documentclass{article}
\usepackage{setspace}
\doublespacing
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{chngcntr}
\usepackage{float}
\usepackage{tabu}
\usepackage{bm}
\usepackage[lite]{amsrefs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{hyperref}\usepackage{xcolor}
%\graphicspath{ {./img/} }


\counterwithin*{equation}{section}

\newcommand{\R}{\mathbb{R}}

\makeatletter
\newcommand*\bigcdot{\mathpalette\bigcdot@{1}}
\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\makeatother

\usepackage{afterpage}

\newcommand\blankpage{%
    \null
    \thispagestyle{empty}%
    \addtocounter{page}{-1}%
    \newpage}
    
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

\usepackage[makeroom]{cancel}


\begin{document}


\title{}
\author{}
\date{}

\maketitle

I do not think that the use of macaques in biomedical research can be ethically justified.

To me, equal interests should receive equal consideration, regardless of colour of skin, gender (and lack thereof) or species. Macaques have an interest in not being experimented on (which is an assumption, but to me a reasonable one). They cannot waive this interest, as humans can by providing consent. 

The counter argument I can foresee is that the research could save many lives. If the research is indeed that important, I do not see why humans would not volunteer. If  the research is not worth volunteering for, it is not worth disregarding the interests of macaques. Experimenting on macaques because humans failed to volunteer would signal to me that the research is not worth the sacrifice, doubly so when the sacrifice forced upon another creature without their consent. 



		
		
		
		
\end{document} 